BLAST: Block Applications for Things

### 2022-04-08 demo-eswc22/paper.tex
Update demo-eswc22/paper.tex
Co-authored-by: Thomas Wehr <derwehr@gmail.com>

\section{Usability Evaluation }
There is a large number of standardized questionnaires in the scientific literature that allow test users to evaluate the usability of a software product. We use the System Usability Scale (SUS) questionnaire to evaluate the user-friendliness of BLAST. According to Assila et al. \cite{assila2016standardized}, SUS provides reliable results over different sample sizes and converges fast to the correct conclusion.

>>>>

\section{Usability Evaluation }
For evaluating the usability of BLAST, we employ the System Usability Scale (SUS) questionnaire. According to Assila et al. \cite{assila2016standardized}, SUS provides reliable results over different sample sizes and converges fast to the correct conclusion.
